---
title: "Data wrangling and stats"
author: "Maximilian H.K. Hesselbarth"
date: "2022-06-30 / 2022-07-01"
output:
  html_document:
    theme: cosmo
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First, load all the packages you want to use. This includes `dplyr`

```{r libs, message = FALSE, warning = FALSE}

# Add code here

```

First, import the _penguins_raw.csv_ data and save it into an object. Use a text editor to check out the column separator and header information of the columns. If you want, try out to convert the _data.frame_ as a _tibble_ using `as_tibble()` from the _tibble_ packages. A _tibble_ is just a "fancy" _data.frame_, but basically the same thing.

```{r read_table}

# Add code here

```

Next, create three new columns in which you convert the culmen length, culmen depth and flipper length from mm to inch. 

```{r convert_col}

# Add code here

```

Now, create new _data.frame_ in which only individuals with a body mass above the third quantile of all body masses are include. 

```{r quantile_filter}

# Add code here

```

Next, calculate at least three descriptive statistics (e.g., mean, min, max, median, quantiles) of the flipper length. Try to calculate them for the whole data set, but also separated by species. 

```{r descriptive}

# Add code here

```

Look at the flipper length (in mm or inch) and test if there is a difference between between the different species.

```{r post_hoc}

# Add code here

```

Pick one species and create a new _data.frame_ containing only the species you selected. Continuous with this sub-selection for the rest of this exercise.

```{r t_test}

# Add code here

```

Last, pick two numeric columns of your choice and try to fit a linear regression model to the data. Is the relationship significant and what do the coefficients mean?

```{r lm}

# Add code here

```
