---
title: "Exercise Basic introduction"
author: "Maximilian H.K. Hesselbarth"
date: "2022-06-30 / 2022-07-01"
output:
  html_document:
    theme: cosmo
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

# RMarkdown

This a a _RMarkdown_ file, which allows to combine text and _R_ code chunks. You can "knit" this file as a _.html_-file by clicking the "knit" button in _RStudio_. Open the file with a web browser to see a rendered version.

Go through this document and try solve the exercise by adding code to the empty code chunks!

# Running basic R code

First, run the following code. To do this, put the cursor into the line you want to run and either click the "Run" button or using the shortcut <CMD/STRG + ENTER>. In order to run multiple lines of code, highlight all lines you want to run.

```{r calculator}
14 + 5.5

(23 - 5) / (4 * 5) ^ 2

50 < 100 & 100 > 200

50 < 100 | 100 > 200
```

# Create objects

Create one character vector storing the name of the following countries: Indonesia, Australia, Madagascar, Brazil, Mexico. 

Next create three more numeric with the number of endemic species [Source](https://ourworldindata.org/biodiversity-and-wildlife)).

1) mammals: 295, 255, 213, 203, 152
2) birds: 525, 359, 119, 254, 120
3) amphibian:  213, 209, 312, 548, 284

```{r objects}

# Add code here

```

Now, combine the three numeric vectors as a `matrix`, in which rows correspond to the different countries and the columns correspond to the different taxonomic groups (Hint: have a look at `?cbind` and/or `?matrix`). What happens if you also add the countries vector to the matrix?

Alternatively, create a `data.frame()` combining all four vectors. What's the difference to the `matrix`?

(Tip: You can always use `class(<object_name>)` to check data structure of an object.)

```{r matrix}

# Add code here

```

Last, use either the `matrix` or the `data.frame` and subset the row with the highest number of amphibian. You have several options to do this. Have a look at e.g., `max()` or `which()`

```{r subset}

# Add code here

```

# Functions

You already used a few functions up to here. To get a bit more used to this, calculate the mean number of species per taxonomic group and round the result to one digit. For this, use `mean()` and `round()`. Bonus point if you can also calculate the mean number of endemic species **per country**.

```{r mean_round}

# Add code here

```

Now, create your own function that takes a vector as input argument and standardizes each element by dividing it by the maximum value and multiplied by 100. Apply the functions to one or several of the endemic species counts. Remember, functions can be created using `function()` and defining arguments and function body.

```{r function}

# Add code here

```
