---
title: "Data vizualisation"
author: "Maximilian H.K. Hesselbarth"
date: "2022-06-30 / 2022-07-01"
output:
  html_document:
    theme: cosmo
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = "center")
```

For this exercise, we are going to use the already cleaned data set from the _palmerpenguins_ package again. Thus, load all packages you need first. 

```{r libs, message = FALSE, warning = FALSE}

# Add code here

```

Create a scatter plot using the two numerical variables you picked in the last exercise to fit a linear regression model. Plot the data (for all species) using point colors that refer to the island the data was collected. Use a solid triangle as point shape. 

```{r, scatter}

# Add code here

```

Now fit the linear regression model again, and add the regression line to the figure.

```{r lm}

# Add code here

```

Create a boxplot of the difference between islands of the body size. Try to also add the raw data points to the boxplot. 

```{r}

# Add code here

```

Try to find out how to export the at least one figure as a PDF file. 

```{r eval = FALSE}

# Add code here

```
